The role of advection versus diffusion in intraventricular transport

### 2025-03-03 paper/main.tex
Formatting tweaks. This template still hurts my eyes.

\pagestyle{fancy}
\rhead{\includegraphics[width=2.5cm]{vch-logo.png}}

\title{The Role of Advection Versus Diffusion in Intraventricular Transport}

\maketitle

% Author: Please give full first and last names for authors and
% include * after the name of all corresponding authors

\author{Halvor Herlyng*}
\author{Ada J.~Ellingsrud}
\author{Miroslav Kuchta}
\author{Inyoung Jeong}
\author{Marie E.~Rognes} \\
\author{Nathalie Jurisch-Yaksi*}

% Affiliations: Please provide adacemic titles (Prof. or Dr.) for all authors where applicable,
% and include an institutional email address for all corresponding authors
\begin{affiliations}
H.~Herlyng, Dr.~A.~J.~Ellingsrud, Dr.~M.~Kuchta, Dr.~M.~E.~Rognes\\
Department of Numerical Analysis and Scientific Computing,
Simula Research Laboratory, Kristian Augusts gate 23, 0164 Oslo, Norway\\
Email Address: hherlyng@simula.no
\\
Dr.~M.~E.~Rognes\\
K.~G.~Jebsen Center for Brain Fluid Research, Oslo, Norway
\\
Dr.~I.~Jeong, Dr.~N.~Jurisch-Yaksi\\
Department of Clinical and Molecular Medicine,
Norwegian University of Science and Technology, Erling Skjalgsons gate 1, 7491 Trondheim, Norway \\
Email Address: nathalie.jurisch-yaksi@ntnu.no

>>>>

%\pagestyle{fancy}
%\rhead{}%\includegraphics[width=2.5cm]{vch-logo.png}}
\pagestyle{plain} % MER

\title{The role of advection versus diffusion in intraventricular transport}
%
\maketitle
%
% Author: Please give full first and last names for authors and
% include * after the name of all corresponding authors
%
\author{Halvor Herlyng*},
\author{Ada J.~Ellingsrud},
\author{Miroslav Kuchta},
\author{Inyoung Jeong},
\author{Marie E.~Rognes}, 
\author{Nathalie Jurisch-Yaksi*}

% Affiliations: Please provide adacemic titles (Prof. or Dr.) for all authors where applicable,
% and include an institutional email address for all corresponding authors
\begin{affiliations}
\noindent H.~Herlyng, Dr.~A.~J.~Ellingsrud, Dr.~M.~Kuchta, Dr.~M.~E.~Rognes\\
Department of Numerical Analysis and Scientific Computing,
Simula Research Laboratory, Kristian Augusts gate 23, 0164 Oslo, Norway\\
Email Address: hherlyng@simula.no \\ 
Dr.~M.~E.~Rognes \\
K.~G.~Jebsen Centre for Brain Fluid Research, Oslo, Norway \\
Dr.~I.~Jeong, Dr.~N.~Jurisch-Yaksi\\
Department of Clinical and Molecular Medicine,
Norwegian University of Science and Technology, Erling Skjalgsons gate 1, 7491 Trondheim, Norway \\
Email Address: nathalie.jurisch-yaksi@ntnu.no
